A Case Study in Preserving a High Energy Physics Application

### 2014-03-03 paper.tex
evalution platform introduction

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Evaluation}
\subsection{Relationship of Different Solutions}
The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}. The aim is to make it easier to repeat one program through making the data and software preparation easier.

>>>>

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Evaluation}
The section first illustrates the relationship of different preservation and reproduction solutions, then the platform used to evaluate different solutions is introduced. The execution time and data size of Solution 2 and 4 are tested and compared. It is hard to accurately calculate the time consumption of Solution 1. Solution 3 shares the same time consumption and data size with Solution 3.

\subsection{Relationship of Different Solutions}
The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}. The aim is to make it easier to repeat one program through making the data and software preparation easier.

\subsection{Evaluation Platform}

The first three solutions are all directly verified on the machine the original
author used to execute the experiment, which is convenient but involves access
authority problem. Solution 4 is verified on the original machine and on one virtual machine.
To compare the execution time and data size of Solution 4
with Solution 2, the package generated on the original machine is utilized to
rerun the experiment on the original machine. This choice avoids the impact of
different CPUs of the original machine and the new machine to repeat the
experiment. To completely verify the correctness of Solution 4, one virtual
machine sharing the same kernel version with the original machine is deployed.
Then the necessary software environment is configured on the virtual machine,
and the package together with the map file are copied onto it, and the
experiment is repeated on the virtual machine.
